Maenpuen et al.~Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2021-12-21 ms/LMA_method.Rmd
updated author info

Phisamai Maenpuen^1,2,3^,
Masatoshi Katabuchi^1,\*^,
Yusuke Onoda^4^,
Cong Zhou^1,2^,
Jiao-Lin Zhang^1,3\*^,
Ya-Jun Chen^1,3,5^

@@

>>>>

Phisamai Maenpuen^1,2,3\*^,
Masatoshi Katabuchi^1,\*^,
Yusuke Onoda^4^,
Cong Zhou^1,2^,
Jiao-Lin Zhang^1,3^,
Ya-Jun Chen^1,3,5^

@@

\* These authors contributed equally to this work.
